\documentclass{book}

\usepackage{graphicx}
\usepackage{float}
\usepackage{amssymb,amsmath}
\newcommand{\bm}[1]{\boldsymbol{#1}}




\usepackage{multirow}
\usepackage{fullpage}
\usepackage{appendix}
\usepackage{setspace}

\usepackage[bf, small, center]{caption}
\setlength{\belowcaptionskip}{10pt}
\usepackage{longtable}

\usepackage{geometry}
\geometry{
%  top=1.0in,  
%  inner=1.5in,
%  outer=1.5in,
  bottom=1.2in,
%  headheight=3ex, 
  headsep=3ex,         
}

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhead[LO, RE]{\rightmark}
\fancyhead[LE, RO]{\thepage}
\fancyfoot[]{}
%\renewcommand{\headrulewidth}{0.3pt}

\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}



\usepackage[phd]{thesisfrontmatter}

% *** NOTE WHICH PROGRAM GENERATED IMAGES OR WHICH POWER POINT THEY ARE FROM
%compare methodology with script for final process
%how much detail in methodology?
%some sort of processing flowchart?
%how much do we care about processing?

\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent


\usepackage{mathtools}
\usepackage{epstopdf}

\usepackage{color}
\usepackage{soul}



\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

\let\stdsection\chapter  
\renewcommand\chapter{\newpage\stdsection}  

%%%%%%%%%%% for Appendix
\makeatletter
\newcommand\appendix@section[1]{%
  \refstepcounter{section}%
  \orig@section*{Appendix \@Alph\c@section: #1}%
  \addcontentsline{toc}{section}{Appendix \@Alph\c@section: #1}%
}
\let\orig@section\section
\g@addto@macro\appendix{\let\section\appendix@section}
\makeatother


%%%%%%%%%%%%%%

\usepackage{hyperref}
\hypersetup{
    bookmarks=true,         % show bookmarks bar?
    unicode=false,          % non-Latin characters in AcrobatÕs bookmarks
    pdftoolbar=true,        % show AcrobatÕs toolbar?
    pdfmenubar=true,        % show AcrobatÕs menu?
    pdffitwindow=false,     % window fit to page when opened
    pdfstartview={FitH},    % fits the width of the page to the window
    pdftitle={WV-2 In Water Component Retrieval },    % title
    pdfauthor={Javier Concha},     % author
    pdfsubject={Subject},   % subject of the document
    pdfcreator={Creator},   % creator of the document
    pdfproducer={Producer}, % producer of the document
    pdfkeywords={keyword1} {key2} {key3}, % list of keywords
    pdfnewwindow=true,      % links in new window
    colorlinks=true,       % false: boxed links; true: colored links
    linkcolor=blue,          % color of internal links
    citecolor=green,        % color of links to bibliography
    filecolor=magenta,      % color of file links
    urlcolor=cyan           % color of external links
}

\usepackage[all]{hypcap} % to see figure with hyper ref

\setcounter{secnumdepth}{5}
\setcounter{tocdepth}{5}

% Added 11-12-13 ----------------------------------------

\usepackage{titlesec} % For the spacing after and before chapter title

\titleformat{\chapter}[display]
    {\normalfont\huge\bfseries}{\chaptertitlename\ \thechapter}{10pt}{\Huge}
\titlespacing*{\chapter}{0pt}{40pt}{20pt}

\usepackage{indentfirst}
\setlength{\parindent}{20pt}
\doublespacing
% Added 11-13-13 ----------------------------------------
% Select what to do with todonotes: 
% \usepackage[disable]{todonotes} % notes not showed
\usepackage[draft]{todonotes}   % notes showed
%******************************************************************************************************

\begin{document}

\degreetitle{The Use of Landsat-8 for Monitoring of Fresh and Coastal Water}
\degreeauthor{Javier A. Concha}
\degreedate{\today{}}
\prevdegreeA{M.S. Rochester Institute of Technology, 2012}
\advisor{Dr. John R. Schott}
\memberA{Dr. Anthony Vodacek}
\memberB{Dr. Aaron Gerace}
\memberC{Dr. Emmett Ientilucci}
\memberD{Dr. Christy Tyler}

\makeproposaldeclaration
\makePHDproposalapproval
% \makecopyright


% \maketitle

\pagenumbering{roman}

% \chapter*{Abstract}
% \addcontentsline{toc}{chapter}{Abstract}

\begin{abstract}
\setlength{\parindent}{20pt}
The Landsat Data Continuity Mission (LDCM; a.k.a. Landsat-8), recently launched (February 2013), is the next generation of Landsat satellite and continues with more than 40 years of continuing imaging acquisition, playing a critical role in monitoring, understanding and managing natural resources such as water. Landsat-8, with its improved spectral bands and radiometric resolution, has the potential to dramatically improve our ability to simultaneously retrieve the three primary coloring agents, chlorophyll (Chl), colored dissolved organic material (CDOM) and suspended material (SM) from water bodies. This work presents the results obtained so far. To date, the method has been tested on Landsat-5 images because Landsat-8 images are still not available.

In the Case 2 water problem, the sensor-reaching signal due to water is very small when compared to the signal due to the atmospheric effects. Therefore, adequate atmospheric correction becomes an important first step to accurately retrieving water parameters. As a first approach, a model based empirical line method (ELM) atmospheric correction method converts sensor-reaching radiance to water leaving reflectance. This model employs pseudo invariant feature (PIF) pixels extraction from Landsat images along with an in water radiative transfer model (HydroLight) to obtain the field spectra. Further atmospheric compensation technique will be investigated.

A look-up-table (LUT) methodology is implemented to retrieve the water parameters. The LUT is created using HydroLight.

Collections of water samples when the satellite passes over the Rochester area are planned for summer 2013. Concentration and inherent optical properties (IOPs) measurement will help to validate the methods.

\end{abstract}

% \chapter*{Acknowledgements}
%*****************************************************************************************************
\begin{acknowledgements}
\setlength{\parindent}{20pt}
To my parents. USGS. Monroe County Environment: Scott, Providencia and Gary. Nina and Rolo. Dr. Christy Taylor. Paul. Aaron Gerace. Alan Wiedmman. Ocean Color community: Emmanuel Boss and attendants of the 2013 Ocean color and instrumentation summer course at the Darling Marine Center. Fulbright commission. My advisor Dr. John Schott. Amanda and Cindy.
\end{acknowledgements}
%*****************************************************************************************************

\tableofcontents

\listoffigures
\addcontentsline{toc}{chapter}{List of Figures}

\listoftables
\addcontentsline{toc}{chapter}{List of Tables}

\include{Introduction}
\include{Objectives}
% \input{Background_and_Theory.tex}
% \input{Methodology.tex}
% \input{Results.tex}
% \input{Future_Work.tex}
% \input{Appendix.tex}

\listoftodos

%\bibliographystyle{ieeetr}
%\bibliographystyle{unsrtnat}
\bibliographystyle{apalike}

\bibliography{/Users/javier/Desktop/Javier/PHD_RIT/Latex/javier_bib}


\end{document}  